---
title: "TidyTemplate"
date: 2024-05-03
output: html_document
---

# Worldwide Bureaucracy Indicators


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(camcorder)
library(here)
library(glue)
library(ggtext)
library(showtext)
library(extrafont)
library(geomtextpath)

```



```{r}
tt_source <- "Worldwide Bureaucracy Indicators"
bg_color <- "#ffffff"
txt_color <- "black"
txt_color2 <- "#20C29D"

yellow <- "#FFB702"  
blue <- "#1E9BD5"
green <- "#20C29D"
light_blue <- "#00E7EC"
red <- "#FF5674"

tt_family <- "montserrat"
tt_family_2 <-  "roboto"


font_add_google("Montserrat", tt_family)
font_add_google("Roboto", tt_family_2)

# font_add("fa-brands",
#          regular = here("Assets","Fonts","fontawesome-free-6.4.2-web","webfonts","fa-brands-400.ttf"))
# font_add("fa-solid",
#          regular = here("Assets","Fonts","fontawesome-free-6.4.2-web","webfonts","fa-solid-900.ttf"))
# font_add("fa-regular",
#          regular = here("Assets","Fonts","fontawesome-free-6.4.2-web","webfonts","fa-regular-400.ttf"))
# showtext_auto(enable = T) 

X  <- str_glue("<span style='font-family:fa-brands'>&#xe61b;</span>")
GH <- str_glue("<span style='font-family:fa-brands'>&#xf09b;</span>")
MN <- str_glue("<span style='font-family:fa-brands'>&#xf4f6;</span>")
DT <- str_glue("<span style='font-family:fa-brands'>&#xf1c0;</span>")

tt_caption <- str_glue(
  "Karina Jonina #TidyTuesday 2024-30-04<br>
  {X} @karinajonina {GH} @kjonina {MN} @turdbull<br>
  Data: {tt_source}
  "
)

tt_title_text    <- str_glue("Worldwide Bureaucracy Indicators")

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2024-04-30")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

```{r Wrangle}
wwbi_data <- tt$wwbi_data
wwbi_series <- tt$wwbi_series
wwbi_country <- tt$wwbi_country

```


# Visualize

Using your processed dataset, create your unique visualization.

```{R Setting Saving Options}
camcorder::gg_record(dir = here("outputs","2024-04-30"),
  device = "png",
  width = 8, height = 7,
  units = "in", dpi = 320
  )
```
  
```{r Visualize}

```


